Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-02-09 msc-publication.tex
add w contour plot for gravityWaves-btf
update to use gnuplot 5, start adding exner/theta sample line plot
tweak alignment of figures

\begin{figure}
	\includegraphics[height=2in]{gw-w-btf.png}
	\includegraphics[height=2in]{melvin-7a.png}
%
	\caption{Gravity wave vertical velocities and thermal anomalies from initial thermal profile}
	\label{fig:gw-w}
\end{figure}

@@

\begin{figure}
	\includegraphics[height=2in]{gw-exner-theta.png}
%
	\caption{Vertical sample line of Exner function of pressure and theta to demonstrate Lorenz computational mode}
	\label{fig:gw-exner-theta}
\end{figure}

>>>>

\begin{figure*}
	\centering
	\includegraphics{../msc-publication-fig-gravityWaves/fig-gravityWaves.pdf}
%
	\caption{Gravity wave vertical velocities and thermal anomalies from initial thermal profile}
	\label{fig:gw-w}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics{../msc-publication-fig-gravityWaves-sampleLine/fig-gravityWaves-sampleLine.pdf}
%
	\caption{Vertical profiles of the Exner function of pressure, $\Pi$, and potential temperature, $\theta$, in the gravity waves test.  The computational mode is manifested as a zig-zag in potential temperature on the SnapCol grid.  Results on the SLEVE grid (not shown) are qualitatively the same as those on the BTF grid.}
	\label{fig:gw-exner-theta}
\end{figure}
